---
title: "第十章-作业"
author: "你的名字(你的学号)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 练习题

1. 读入数据`Credit.csv`。
```{r}
credit = read.csv("./data/Credit.csv")
credit = credit[, -1]
```
数据包含如下变量：

- balance: average credit card debt for a number of individuals
- cards: number of credit cards
- education: years of education
- income (in thousands of dollars)
- limit (credit limit)
- rating (credit rating)
- Married (marital status)
- ethnicity (Caucasian, African American or Asian)
- gender
- student (student status)
- age


```{r}
par(mar=c(0,5,0,0))
library(RColorBrewer)
miscolores = brewer.pal(8,"Set2")[1:8]
```

2. 以`Rating`为横轴，`Balance`为纵轴画散点图，横轴坐标名称为`Rating`，纵轴坐标名称为`Balance`。点的性质为`+`。

```{r fig.retina=5, fig.align='center', fig.height=5, fig.width=7}
plot(credit$Rating, credit$Balance, pch=3, col=miscolores[2],
     xlab="Rating", ylab="Balance")
```

3. 画出`Balance`的直方图，设置参数`freq=F`。并且画出`Balance`的概率密度函数。注：可能需要用到函数`density()`。

```{r fig.retina=5, fig.align='center', fig.height=5, fig.width=7}
hist(credit$Balance, col=miscolores[2], breaks=20, freq=F, xlab="Balance", main="Histogram of Balance")
d = density(credit$Balance)
lines(d, lwd=3, col=miscolores[1])
```


4. 画出学生的`Balance`的箱型图和非学生的`Balance`的箱型图。两个箱型图分别用两种不同的颜色表示。

```{r fig.retina=5, fig.align='center', fig.height=5, fig.width=7}
boxplot(Balance~Student, data=credit, col=miscolores[1:2])
```










